Declarative Pearl: Lightweight Probabilistic Programming in Curry

### 2015-08-14 Paper/paper.tex
Add introductory example for bayesian network in Curry

>>>>

Experts often state that you do not need to be a rocket scientist in
order to make sense of research results; however, in the area of
machine learning, beginners often face difficulties to use the tools
and current knowledge for their own project. %
That is, beginners need to inverse many hours to digest technical
details before they can actually make use of top-of-the-art models and
algorithms. %

In the field of programming languages, the community often tries to
generalise and simplify commen concepts and repetative structures. %
Fortunately, the rising collaboration between ML and PL communities
has produced a number of programming languages and libraries for
probabilistic programming that aim at minimising the obstacle to use
practicle results of ML, thus, empower more users to apply ML
techniques to their problems. %

For instance, a typical problem in the field of \emph{Bayesian
  Network}s is to transfer a given model (e.g., a conditional
probability table) into code in order to evaluation the model for a
given data set. %
Such an evaluation can range from stating queries to documenting
observations to apply learning algorithms. %

\begin{figure}
\caption{Bayesian network with conditional probability table for \emph{alarm}-scenario}
\end{figure}

We can model this bayesian network with the following code. %

\begin{verbatim}
earthquake = bernoulli 0.2
burglary   = bernoulli 0.7

alarm True  True  = bernoulli 0.9
alarm True  False = bernoulli 0.8
alarm False True  = bernoulli 0.1
alarm False False = bernoulli 0.0
\end{verbatim}

The definition for the probabilistic functions \code{earthquake},
\code{burglary} and \code{alarm} follow straight-forward from the
scheme of the given model. %
The function \code{bernoulli} yields a probabilistic value that is
\code{True} with probability given by the first argument and
\code{False} with probability $1 - prob$. %

\begin{verbatim}
bernoulli prob = mkDist True prob
bernoulli prob = mkDist False (1.0 - prob)
\end{verbatim}
